### 2014-06-16 kypchak-morphfest-2014/poster.tex
more work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@54486 72bbbca6-d526-0410-a7d9-f06f51895060

	\headerbox{Morphological transducers}{name=morphtrans,below=kypchaklgs}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)
		\end{itemize}
		\scalebox{0.96}{
			`алдым' \hilitetwo{↔} \texttt{ал{\small <v><tv><ifi><p1><sg>}}, \texttt{алд{\small <n><px1sg><nom>}}
		}

@@

	\headerbox{Development effort}{name=devel,below=adjectives,column=1}{

@@

		\headerbox{Evaluation}{name=coverage,span=1,column=3,row=0}{

@@

%		\scalebox{0.8}{
%			\begin{tabular}{lll}
%				\toprule
%				\textbf{type} & \textbf{lang} & \textbf{contents} \\ % & \textbf{origin} \\
%				\midrule
%				Encyclopædic & kaz & Wikipedia \\ % wpdump & 20131006 \\
%					& tat & Wikipedia \\ % wpdump & 20130225 \\
%					& kum & — \\ % — & — \\
%				\midrule
%				News & kaz & RFE/RL (azattyq.org) \\ % RFE/RL & azattyq.org 2010 \\
%					& tat & tat.tatar-inform.ru \\ % Татар-информ & tat.tatar-inform.ru 2005-2011 \\
%					& kum & Ёлдаш (yoldash.etnosmi.ru) \\ % Ёлдаш & yoldash.etnosmi.ru \\
%				\midrule
%				Religion & kaz & Quran + Bible \\ % quran + bible & kkitap.net, kuran.kz \\
%					& tat & Quran + New Testament \\ % quran + nt & ibt.org.ru, tanzil.net \\
%					& kum & Genesis + New Testament \\ % genesis + nt & ibt.org.ru \\
%				\bottomrule
%			\end{tabular}
%		}
		\scalebox{0.77}{
			\begin{tabular}{llll}
				\toprule
					& \textbf{Wikipedia} & \textbf{News} & \textbf{Religion} \\
				\midrule
					\texttt{\textbf{Kyrgyz}} & Wikipedia & azattyk.org & Quran + Bible \\
					\texttt{\textbf{Kazakh}} & Wikipedia & azattyq.org & Quran + Bible \\
					\texttt{\textbf{Tatar}} & Wikipedia & tat.tatar-inform.ru & Quran + New Testament \\
					\texttt{\textbf{Kumyk}} & --- & yoldash.etnosmi.ru & Genesis + New Testament \\
				\bottomrule
			\end{tabular}

@@

				\multirow{4}{*}{\textbf{Kyrgyz}} & Wikipedia & M &  $\pm$  &  \\
					&  &  &  $\pm$  &  \\\cmidrule{2-5}
				 (r54474) & Average &  & \hiliteone{} $\pm$  &  \\
				\midrule
				\multirow{4}{*}{\textbf{Kazakh}} & Wikipedia & 25.6M & 85.61 $\pm$ 1.37 & 2.43 \\
					& News & 3.8M & 92.12 $\pm$ 2.72  & 2.88 \\
					& Religion & 851K & 92.49 $\pm$ 1.66  & 2.63 \\\cmidrule{2-5}
				 (r50547) & Average &  & \hiliteone{90.07} $\pm$ 1.91  & 2.64\\
				\midrule
				\multirow{4}{*}{\textbf{Tatar}} & Wikipedia & 159K & 86.35 $\pm$ 2.17  & 2.24\\
					& News & 5.2M & 89.75 $\pm$ 0.07  & 2.30 \\
					& Religion & 382K & 91.25 $\pm$ 2.55 & 2.24 \\\cmidrule{2-5}
				 (r50260) & Average &  & \hiliteone{89.12} $\pm$ 1.60 & 2.26 \\
				\midrule
				\multirow{3}{*}{\textbf{Kumyk}} & News & 286K &  91.10 $\pm$ 0.86  & 1.53 \\
					& Religion & 227K & 92.47 $\pm$ 1.03  & 1.53 \\\cmidrule{2-5}
				 (r50300) & Average &  & \hiliteone{91.78} $\pm$ 0.94 & 1.53 \\
				\bottomrule
			\end{tabular}\\
		}
			%}
			%%\end{centering}
%		}

@@

			\vspace{-1em}
			\begin{center}
				\begin{tabular}{lrrr}
				\toprule
					\textbf{Language} & \textbf{Forms} & \textbf{Precision} (\%) & \textbf{Recall} (\%) \\
				\midrule
					Kazakh & 1000 & 98.61 &  57.98 \\
					Tatar & 1000 & 95.03 & 85.65 \\
					Kumyk & 500 & 96.57 & 69.11 \\
				\bottomrule
				\end{tabular}
			\end{center}

@@

		\headerbox{Orthography-phonology mapping issues}{name=twol,column=2,below=exout}{
			\htwo{Ambiguous characters}
			\begin{itemize}
				\item Have front- and back-vowel readings in native words
			\end{itemize}

@@

%			\htwo{Vowel harmony}
%			\begin{itemize}
%				\item two basic vowel archiphonemes:
%				\begin{itemize}
%					\item high vowel, \texttt{\{I\}}; [±back] and [±round] from prev.\ V\\
%		\begin{tabular}{ccccc}
%			\toprule
%			after & result & & after & result \\
%			\midrule
%			{\qipa и} & {\qipa и} & & {\qipa ы} & {\qipa ы} \\
%			{\qipa ү} & {\qipa ү} & & {\qipa у} & {\qipa у} \\
%			{\qipa е} & {\qipa и} & & {\qipa а} & {\qipa ы} \\
%			{\qipa ө} & {\qipa ү} & & {\qipa о} & {\qipa у} \\
%			\bottomrule
%		\end{tabular}
%					\item low vowel, \texttt{\{A\}}; [±back] and [±round] from prev.\ V\\
%					with one important exception: after \hilitetwo{у}\\
%		\begin{tabular}{ccccc}
%			\toprule
%			after & result & & after & result \\
%			\midrule
%			{\qipa и} & {\qipa е} & & {\qipa ы} & {\qipa а} \\
%			{\qipa ү} & {\qipa ө} & & {\qipa \hilitetwo{у}} & {\qipa \hilitetwo{а}} \\
%			{\qipa е} & {\qipa е} & & {\qipa а} & {\qipa а} \\
%			{\qipa ө} & {\qipa ө} & & {\qipa о} & {\qipa о} \\
%			\bottomrule
%		\end{tabular}
%
%
%				\end{itemize}
%				\item take backness and roundness of previous vowel\\
%				exception: 
%
%			\end{itemize}

%			\htwo{Desonorisation}
%\begin{itemize}
%	\item {\texttt \{N\}} desonorises to д after a consonant\\
%		алма-\hiliteone{\{N\}}\{I\} → алма\hiliteone{н}ы \eng{apple--\gmk{ACC}} \\
%		сыр-\hiliteone{\{N\}}\{I\} → сыр\hiliteone{д}ы \eng{secret--\gmk{ACC}}
%	\item {\texttt \{L\}} desonorises to д after cons.\ of sonority ≤ /l/ \\
%		сыр-\hiliteone{\{L\}}\{A\}р → сыр\hiliteone{л}ар \eng{secret--\gmk{PL}} \\
%		кыз-\hiliteone{\{L\}}\{A\}р → кыз\hiliteone{д}ар \eng{girl--\gmk{PL}} \\
%\end{itemize}
%
%	\vspace{-0.5ex}
%\codeex{
%			\texttt{"L Desonorisation"\\
%			\%\{L\%\}:д <=> :VoicedLowSonCns \%>:\ \blank{1em} ;}\\
%			
%			\texttt{"N Desonorisation"\\
%			\%\{N\%\}:д <=> :VoicedCns \%>:\ \blank{1em} ;}
%}
%
%			\htwo{Lenition}
%\begin{itemize}
%	\item Turn {\texttt \{y\}} into a harmonised high vowel when a vowel doesn't follow the following consonant:\\
%	мур\{у\}н → мурун \eng{nose}\\
%	мур\{у\}н+\{I\}м → мурдум \eng{my nose}\\
%\end{itemize}
%	\vspace{-0.5ex}
%\codeex{
%{\small \texttt{\%\{y\%\}:Vy <=> [ :LastVowel :Cns* :Cns ]/[:0] \blank{1em}\\
%	\vspace{-0.5ex}\hspace{1pt}\hfill{} [ :Cns [ .\#.\ | :Cns ] ]/[ :0 | \%>:]\ ;\\
%  \vspace{-0.5ex}\hspace{1ex}where  Vy  in  (  и  ү  и  и  ү  ы  ы  у  у  ы  у  у )\\
%  \vspace{-0.5ex}LastVowel  in  (  и  ү  е  э  ө  я  а  ё  о  ы  ю  у )\\
%  \vspace{-0.5ex}\hspace{12ex}         matched ;}}
%}
%
%			%\htwo{Nouns ending in /рн/}
%
%			\htwo{й+vowel letters}
%			\begin{itemize}
%				\item{} [ а о у ] become [ я ё ю ] after й and й deletes
%				\item й incorporated into the context of many rules
%				\item + separate rules to change the characters
%				\item + a rule to delete the original й\\
%			\end{itemize}
%	\vspace{-1ex}
%
%				\codeex{
%					\texttt{"Deletion of й before yoticised vowels"\\
%					й:0 <=> \blank{1em} [ :YotVow ]/[ :0 | \%>:\ ]\ ;}
%				}
%		}

		\headerbox{Ongoing and future work}{name=nedostatki,column=5}{
			\begin{itemize}
%				\item case changes for words with one root\\
%					\hiliteone{Ф}инландия \eng{Finland}, \hiliteone{ф}инландиялык \eng{Finnish}
%				\item phonol.\ (vowel harmony, desonorisation) with abbrevs.\\
%					АКШ [акышы] \eng{USA} → АКШ\hiliteone{н}ын / *АКШ\hiliteone{т}ын
%				\item vowel harmony with numbers\\
%					{\qipa 100 [жүз] → 100дүн [жүздүн] / *100нын}
%				\item compound verbs (esp.\ ones with changeable parts)
%				\item gerunds with mono-syllabic V-final verbs\\
%					{\qipa иште- \eng{work} → иштеш / иштөө \eng{working}}\\
%					{\qipa же- \eng{eat} → жеш / *жөө \eng{eating}}
				\item Disambiguation, more stems
				\item Clean up Kyrgyz transducer
				\item Machine translation between these languages
				\item Bring our other Kypchak transducers to comparable performance:\\
				Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				\item Other Turkic lgs.:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
			%\vspace{0.98em}
		}

@@

>>>>

	\headerbox{Morphological transducers}{name=morphtrans,below=kypchaklgs}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Efficient (in speed \& size) models of a language's morphology
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)
		\end{itemize}
		\scalebox{0.96}{
			`алдым' \hilitetwo{↔} \texttt{ал{\small <v><tv><ifi><p1><sg>}}, \texttt{алд{\small <n><px1sg><nom>}}
		}

@@

	\headerbox{Development effort}{name=devel,column=4,row=0}{

@@

		\headerbox{Evaluation}{name=coverage,span=1,column=5,row=0}{

@@

%		\scalebox{0.8}{
%			\begin{tabular}{lll}
%				\toprule
%				\textbf{type} & \textbf{lang} & \textbf{contents} \\ % & \textbf{origin} \\
%				\midrule
%				Encyclopædic & kaz & Wikipedia \\ % wpdump & 20131006 \\
%					& tat & Wikipedia \\ % wpdump & 20130225 \\
%					& kum & — \\ % — & — \\
%				\midrule
%				News & kaz & RFE/RL (azattyq.org) \\ % RFE/RL & azattyq.org 2010 \\
%					& tat & tat.tatar-inform.ru \\ % Татар-информ & tat.tatar-inform.ru 2005-2011 \\
%					& kum & Ёлдаш (yoldash.etnosmi.ru) \\ % Ёлдаш & yoldash.etnosmi.ru \\
%				\midrule
%				Religion & kaz & Quran + Bible \\ % quran + bible & kkitap.net, kuran.kz \\
%					& tat & Quran + New Testament \\ % quran + nt & ibt.org.ru, tanzil.net \\
%					& kum & Genesis + New Testament \\ % genesis + nt & ibt.org.ru \\
%				\bottomrule
%			\end{tabular}
%		}
		\scalebox{0.77}{
			\begin{tabular}{llll}
				\toprule
					& \textbf{Wikipedia} & \textbf{News} & \textbf{Religion} \\
				\midrule
					\texttt{\textbf{Kyrgyz}} & Wikipedia & azattyk.org & Quran + Bible \\
					% 2013-05-30, 2010, 
					\texttt{\textbf{Kazakh}} & Wikipedia & azattyq.org & Quran + Bible \\
					\texttt{\textbf{Tatar}} & Wikipedia & tat.tatar-inform.ru & Quran + New Testament \\
					\texttt{\textbf{Kumyk}} & --- & yoldash.etnosmi.ru & Genesis + New Testament \\
				\bottomrule
			\end{tabular}

@@

				\multirow{4}{*}{\textbf{Kyrgyz}} & Wikipedia & M & 84.51 $\pm$ 2.27 &  \\
					& News &  & 91.43 $\pm$ 0.51 &  \\
					& Religion &  &  $\pm$  &  \\\cmidrule{2-5}
				 (r54474) & Average &  & \hiliteone{} $\pm$  &  \\
				\midrule
				\multirow{4}{*}{\textbf{Kazakh}} & Wikipedia & 25.6M & 85.61 $\pm$ 1.37 & 2.43 \\
					& News & 3.8M & 92.12 $\pm$ 2.72  & 2.88 \\
					& Religion & 851K & 92.49 $\pm$ 1.66  & 2.63 \\\cmidrule{2-5}
				 (r50547) & Average &  & \hiliteone{90.07} $\pm$ 1.91  & 2.64\\
				\midrule
				\multirow{4}{*}{\textbf{Tatar}} & Wikipedia & 159K & 86.35 $\pm$ 2.17  & 2.24\\
					& News & 5.2M & 89.75 $\pm$ 0.07  & 2.30 \\
					& Religion & 382K & 91.25 $\pm$ 2.55 & 2.24 \\\cmidrule{2-5}
				 (r50260) & Average &  & \hiliteone{89.12} $\pm$ 1.60 & 2.26 \\
				\midrule
				\multirow{3}{*}{\textbf{Kumyk}} & News & 286K &  91.10 $\pm$ 0.86  & 1.53 \\
					& Religion & 227K & 92.47 $\pm$ 1.03  & 1.53 \\\cmidrule{2-5}
				 (r50300) & Average &  & \hiliteone{91.78} $\pm$ 0.94 & 1.53 \\
				\bottomrule
			\end{tabular}\\
		}
			%}
			%%\end{centering}
%		}

@@

			\vspace{-1em}
			\begin{center}
				\begin{tabular}{lrrr}
				\toprule
					\textbf{Language} & \textbf{Forms} & \textbf{Precision} (\%) & \textbf{Recall} (\%) \\
				\midrule
					Kyrgyz & 500 &  &  \\
					Kazakh & 1000 & 98.61 &  57.98 \\
					Tatar & 1000 & 95.03 & 85.65 \\
					Kumyk & 500 & 96.57 & 69.11 \\
				\bottomrule
				\end{tabular}
			\end{center}

@@

		\headerbox{Orthography-phonology mapping issues}{name=twol,column=3}{ %,below=exout}{
			\htwo{Ambiguous characters}
			\begin{itemize}
				\item Have front- and back-vowel readings in native words
			\end{itemize}

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=5,below=coverage}{
			\begin{itemize}
%				\item case changes for words with one root\\
%					\hiliteone{Ф}инландия \eng{Finland}, \hiliteone{ф}инландиялык \eng{Finnish}
%				\item phonol.\ (vowel harmony, desonorisation) with abbrevs.\\
%					АКШ [акышы] \eng{USA} → АКШ\hiliteone{н}ын / *АКШ\hiliteone{т}ын
%				\item vowel harmony with numbers\\
%					{\qipa 100 [жүз] → 100дүн [жүздүн] / *100нын}
%				\item compound verbs (esp.\ ones with changeable parts)
%				\item gerunds with mono-syllabic V-final verbs\\
%					{\qipa иште- \eng{work} → иштеш / иштөө \eng{working}}\\
%					{\qipa же- \eng{eat} → жеш / *жөө \eng{eating}}
				\item Disambiguation, more stems
				\item Clean up Kyrgyz transducer
				\item Machine translation between these languages
				\item Bring other Kypchak transducers to comparable performance:\\
				Qaraqalpaq, Bashqort, Nogay, Crimean Tatar
				\item Other Turkic lgs.:\ Uzbek, Uyghur, Chuvash, Yakut, Tuvan, etc.
			\end{itemize}
			%\vspace{0.98em}
		}

@@

		\headerbox{Morphophonology}{name=morphophon,column=1,below=exout}{
%			\htwo{Vowel harmony}
%			\begin{itemize}
%				\item two basic vowel archiphonemes:
%				\begin{itemize}
%					\item high vowel, \texttt{\{I\}}; [±back] and [±round] from prev.\ V\\
%		\begin{tabular}{ccccc}
%			\toprule
%			after & result & & after & result \\
%			\midrule
%			{\qipa и} & {\qipa и} & & {\qipa ы} & {\qipa ы} \\
%			{\qipa ү} & {\qipa ү} & & {\qipa у} & {\qipa у} \\
%			{\qipa е} & {\qipa и} & & {\qipa а} & {\qipa ы} \\
%			{\qipa ө} & {\qipa ү} & & {\qipa о} & {\qipa у} \\
%			\bottomrule
%		\end{tabular}
%					\item low vowel, \texttt{\{A\}}; [±back] and [±round] from prev.\ V\\
%					with one important exception: after \hilitetwo{у}\\
%		\begin{tabular}{ccccc}
%			\toprule
%			after & result & & after & result \\
%			\midrule
%			{\qipa и} & {\qipa е} & & {\qipa ы} & {\qipa а} \\
%			{\qipa ү} & {\qipa ө} & & {\qipa \hilitetwo{у}} & {\qipa \hilitetwo{а}} \\
%			{\qipa е} & {\qipa е} & & {\qipa а} & {\qipa а} \\
%			{\qipa ө} & {\qipa ө} & & {\qipa о} & {\qipa о} \\
%			\bottomrule
%		\end{tabular}
%
%
%				\end{itemize}
%				\item take backness and roundness of previous vowel\\
%				exception: 
%
%			\end{itemize}

			\htwo{Desonorisation (kaz \& kir)}
				\begin{itemize}
					\item {\texttt \{N\}} desonorises to д after a consonant\\
						алма-\hiliteone{\{N\}}\{I\} → алма\hiliteone{н}ы \eng{apple--\gmk{ACC}} \\
						сыр-\hiliteone{\{N\}}\{I\} → сыр\hiliteone{д}ы \eng{secret--\gmk{ACC}}
					\item {\texttt \{L\}} desonorises to д after cons.\ of sonority ≤ /l/ \\
						сыр-\hiliteone{\{L\}}\{A\}р → сыр\hiliteone{л}ар \eng{secret--\gmk{PL}} \\
						кыз-\hiliteone{\{L\}}\{A\}р → кыз\hiliteone{д}ар \eng{girl--\gmk{PL}} \\
				\end{itemize}

				\vspace{-0.5ex}
				\codeex{
					\texttt{"L Desonorisation"\\
						\%\{L\%\}:д <=> :VoicedLowSonCns \%>:\ \blank{1em} ;}\\

					\texttt{"N Desonorisation"\\
						\%\{N\%\}:д <=> :VoicedCns \%>:\ \blank{1em} ;}
				}

			\htwo{Epenthesis}
				\begin{itemize}
					\item Turn {\texttt \{y\}} into a harmonised high vowel when a vowel doesn't follow the following consonant:\\
					мур\{у\}н → мурун \eng{nose}\\
					мур\{у\}н+\{I\}м → мурдум \eng{my nose}\\
				\end{itemize}
					\vspace{-0.5ex}
\codeex{
{\small \texttt{\%\{y\%\}:Vy <=> [ :LastVowel :Cns* :Cns ]/[:0] \blank{1em}\\
	\vspace{-0.5ex}\hspace{1pt}\hfill{} [ :Cns [ .\#.\ | :Cns ] ]/[ :0 | \%>:]\ ;\\
  \vspace{-0.5ex}\hspace{1ex}where  Vy  in  (  и  ү  и  и  ү  ы  ы  у  у  ы  у  у )\\
  \vspace{-0.5ex}LastVowel  in  (  и  ү  е  э  ө  я  а  ё  о  ы  ю  у )\\
  \vspace{-0.5ex}\hspace{12ex}         matched ;}}
}

%			%\htwo{Nouns ending in /рн/}
%
%			\htwo{й+vowel letters}
%			\begin{itemize}
%				\item{} [ а о у ] become [ я ё ю ] after й and й deletes
%				\item й incorporated into the context of many rules
%				\item + separate rules to change the characters
%				\item + a rule to delete the original й\\
%			\end{itemize}
%	\vspace{-1ex}
%
%				\codeex{
%					\texttt{"Deletion of й before yoticised vowels"\\
%					й:0 <=> \blank{1em} [ :YotVow ]/[ :0 | \%>:\ ]\ ;}
%				}
		}

		\headerbox{Morphotactics}{name=lexc,column=2,below=exout}{
			\htwo{Morphological \& orthographical words}

			\begin{itemize}
				\item{} {\qipa өнүктүрөбүзбү ?} \eng{will we develop [it]?}\\
				\texttt{ өнүк{\small <v><tv><caus><aor><p1><pl>+}бы{\small <qst>}}
				\item{} {\qipa келатсаң} \eng{if you come}\\
				\texttt{кел{\tt {\small <v><iv><prc\_impf>}}+жат{\small <vaux><gna\_cnd><p2><sg>}}
			\end{itemize}

			%\htwo{Irregular negatives of finite verb forms}

			\htwo{Irregular [noun + possessive + case] forms}

			\begin{itemize}
				\item Some combinations of possessive and case morphemes are non-canonical (i.e., not formed simply by concatenation):

			\begin{center}
			\vspace{-0.5em}
{\small
{\qipa		
	\begin{tabular}{llllll}
		\toprule
		case & form & 1SG & 2SG & 3SP  \\
		\midrule
		nom & — & -(I)м & -(I)ң & -(S)I  \\
		acc & -NI & -(I)мдI & -(I)ңдI & -\textbf{(S)Iн}  \\
		gen & -NIн & -(I)мдIн & -(I)ңдIн & -(S)IнIн  \\
		loc & -DA & -(I)мдA & -(I)ңдA & -\textbf{(S)IндA}  \\
		abl & -DAн & -(I)мдAн, & -(I)ндAн, & -\textbf{(S)IнAн}  \\
		~   &     & -\textbf{(I)мAн} & -\textbf{(I)ңAн} \\
		dat & -GA & -\textbf{(I)мA} & -\textbf{(I)ңA} & -\textbf{(S)IнA} \\
		\bottomrule
	\end{tabular}
}}
			\end{center}

%				\item Trade-off:
%				\begin{itemize}
					\item morphophon.\ complicateder, morphotactics simpler
					\item underlying form used: \texttt{\{S\}\{I\}\{n\}}
					\item phonological rules delete \texttt{\{n\}}, \texttt{\{S\}} by context
%				\end{itemize}
			\end{itemize}

			\htwo{Noun-noun compounds}

			\begin{itemize}
				\item one type of N-N compunds: N2 has \texttt{<px3>} and related morphology
			\end{itemize}
			\vspace{0.6ex}
			\codeex{
			{\small
			\texttt{LEXICON N-INFL-3PX-COMPOUND\\
			\vspace{-0.5ex}\%<n\%>:\%>\%\{S\%\}\%\{I\%\}\%\{n\%\} GEN-POS ;}\\

			\texttt{LEXICON Nouns\\
			\vspace{-0.5ex}аба\%\ ырайы:аба\%\ ырай\ N-INFL-3PX-COMPOUND ;\\\vspace{-0.5ex}\hspace{0.1pt}\hfill{}!\ "weather"\\
			\vspace{-0.5ex}чакыруу\%\ кагазы:чакыруу\%\ кагаз\ N-INFL-3PX-\\\vspace{-0.5ex}\hspace{0.1pt}\hfill{}COMPOUND ;\ !\ "invitation"}}
			}

			\vspace{0.5ex}
			%чакыруу кагазы
		}
